Case for Support

### 2021-11-16 application/bonsai.tex
Updates from Overleaf

\textbf{Bonsai}~\citep{lopesEtAl15,lopesAndMonteiro21} is a free and open-source visual programming language developed 
in response to these challenges.
% ~\citep{lopesEtAl15,lopesAndMonteiro21} is a free and open-source visual
% programming language that 
Its design emphasizes performance, flexibility, and ease-of-use,
allowing scientists with no previous programming experience to quickly develop
their own high-performance data acquisition and experimental control systems.
Bonsai combines a high-level event algebra for data streams with an integrated
development environment (IDE) and an extensive library of plugins supporting
multiple hardware and software packages used by the neuroscience research
community (Figure~\ref{fig:bonsai}A-B).
%
A Bonsai graphical program consists of one or more source data streams (e.g. neural activity, video, audio, sensors, etc)
and several interconnected operators that transform input to output
datastreams (Figure~\ref{fig:bonsai}C).

>>>>

\textbf{Bonsai}~\citep{lopesEtAl15,lopesAndMonteiro21} is a free and open-source visual programming language developed 
in response to these challenges.
% ~\citep{lopesEtAl15,lopesAndMonteiro21} is a free and open-source visual
% programming language that 
Its design emphasises performance, flexibility, and ease-of-use,
allowing scientists with no previous programming experience to quickly develop
their own high-performance data acquisition and experimental control systems.
Bonsai combines a high-level event algebra for data streams with an integrated
development environment (IDE) and an extensive library of plugins supporting
multiple hardware and software packages used by the neuroscience research
community (Figure~\ref{fig:bonsai}A-B).
%
A Bonsai graphical program consists of one or more source data streams (e.g. neural activity, video, audio, sensors, etc)
and several interconnected operators that transform input to output
datastreams (Figure~\ref{fig:bonsai}C).
